Holomorphic field theories and higher algebra

### 2023-08-15 highervertexops.tex
tiny tweaks

There is a canonical contracting homotopy 
\beqn
H \colon \sfA \to \sfA[-1]
\eeqn 
because for each $b > 0$, there is a canonical equivariant inverse $\sfR_{a,b} \to \sfR_{a+1,b-1} \omega$.
Explicitly, send the highest weight vector $z_1^{a+1} \lambda_2^{b-1} \omega$ to the highest weight vector $z_1^{a} \lambda_2^{b}$ and then determine where other vector go via the lowering operator.
For $b = 0$, $H|_{\sfR_{0,b}\omega} = 0$.

@@

\begin{lem}
The data $(i,p,H)$ determines a deformation retraction where $i$ is a map of dg commutative algebras.
\end{lem}

>>>>

There is a canonical contracting homotopy $H$ on $\sfA$ 
because for each $b > 0$, there is a canonical equivariant inverse $\sfR_{a,b} \to \sfR_{a+1,b-1} \omega$.
Explicitly, send the highest weight vector $z_1^{a+1} \lambda_2^{b-1} \omega$ to the highest weight vector $z_1^{a} \lambda_2^{b}$ and then determine where other vector go via the lowering operator.
For $b = 0$, $H|_{\sfR_{0,b}\omega} = 0$.

@@

\begin{lem}
The data $(i,p,H)$ determines a special deformation retraction where $i$ is a map of dg commutative algebras.
\end{lem}
